The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area

### 2024-05-09 MS_ToSubmit/RevisedSupMaterial.Rmd
Final Sup Mat

---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
  word_document: default
# classoption: landscape
bibliography: AMPBancoBurdwood.bib
csl: "elsevier-harvard2.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{amsmath}
- \usepackage{pdflscape,booktabs}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \linenumbers
---

@@

```{r, out.width = "12cm", echo = FALSE, message=FALSE, fig.align = 'center', fig.cap = "Matrix of pairwise interactions and the oriented graph (food web) derived from it. Number of species S = 9, number of interactions (L) = 15."}
library(knitr)
knitr::include_graphics("FigS1.png")
```

@@

# Discard low resolution interactions
int_good_res <- int_raw %>% 
  dplyr::filter(!str_detect(Prey, "\\*$")) %>% 
  dplyr::filter(!str_detect(Predator, "\\*$")) %>% 
  mutate(Prey = case_when(Prey == "Brachiopoda_spp" ~ "Brachiopoda", TRUE ~ Prey)) %>%
  dplyr::select(Prey, Predator, Reference, Reference_link) %>% 
  distinct(Prey, Predator, .keep_all = TRUE)

@@

pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Reference_link = paste('\\tiny', Reference_link), Reference = paste('\\tiny', Reference), Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator)) %>% rename("Link"="Reference_link"), style="multiline", split.tables = Inf, justify = c("left","left","center","right"),
             caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")

@@

@@

>>>>

---
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
# classoption: landscape
bibliography: AMPBancoBurdwood.bib
csl: "elsevier-harvard2.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{amsmath}
- \usepackage{pdflscape,booktabs}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \linenumbers
---

@@

```{r, out.width = "12cm", echo = FALSE, message=FALSE, fig.align = 'center', fig.cap = "Matrix of pairwise interactions and the oriented graph (food web) derived from it. Number of species S = 9, number of interactions (L) = 15."}
library(knitr)
knitr::include_graphics("../Figures/Figure S1 final.png")
```

@@

# Discard low resolution interactions
int_good_res <- int_raw %>% 
  dplyr::filter(!str_detect(Prey, "\\*$")) %>% 
  dplyr::filter(!str_detect(Predator, "\\*$")) %>% 
  mutate(Prey = case_when(Prey == "Brachiopoda_spp" ~ "Brachiopoda", TRUE ~ Prey)) %>%
  dplyr::select(Prey, Predator, Reference, Reference_link) %>% 
  distinct(Prey, Predator, .keep_all = TRUE) %>% 
  rename(., Link = Reference_link)

@@

# write.csv(int_good_res %>% arrange(., (Predator)), file = "TableS1_14600.csv")

pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Reference_link = paste('\\tiny', Reference_link), Reference = paste('\\tiny', Reference), Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator)), style="multiline", split.tables = Inf, justify = c("left","left","center","right"),
             caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")

@@

# write.csv(sp_list %>% arrange(., (Species)) %>% rename("Taxonomy"="TaxLevel", "Group"="FunctionalGroup", "Link"="Reference_pres_link"), file = "TableS2_14600.csv")

@@

# write.csv(tbl_3 %>% arrange(., (TotalDegree)) %>% rename("Species"="TrophicSpecies", "Group"="FunctionalGroup", "Degree"="TotalDegree", "TS"="meanTrophicSimil", "TR"="TopRole"), file = "TableS3_14600.csv")
